quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Added langevitour of the model

>>>>

tsne_limb_obj <- fit_highd_model(
  highd_data = data_limb, 
  nldr_data = tsne_limb, 
  bin1 = 19, 
  q = 0.1, 
  benchmark_highdens = 2)

df_bin_centroids_limb <- tsne_limb_obj$model_2d
df_bin_limb <- tsne_limb_obj$model_highd
trimesh_data_limb <- tsne_limb_obj$trimesh_data
tsne_limb_scaled <- tsne_limb_obj$nldr_obj$scaled_nldr

tsne_limb_scaled_with_cluster <- inner_join(tsne_limb_scaled, cluster_df, by = "ID") |>
  mutate(cluster = as.character(cluster.ids))

trimesh_limb <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled_with_cluster,
    aes(
      x = emb1,
      y = emb2,
      color = cluster
    ),
    alpha = 0.3
  ) +
  geom_segment(data = trimesh_data_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  scale_color_manual(values = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494')) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

```{r}
#| label: prep-limb-tsne-author-model-proj

data_limb_n <- data_limb |> 
  select(-ID) |>
  mutate(type = "data")

df_b_limb <- df_bin_limb |>
  dplyr::filter(hexID %in% df_bin_centroids_limb$hexID) |>
  dplyr::mutate(type = "model") ## Data with summarized mean

## Reorder the rows of df_b according to the hexID order in df_b_with_center_data
df_b_limb <- df_b_limb[match(df_bin_centroids_limb$hexID, df_b_limb$hexID),] |>
  dplyr::select(-hexID)

# Apply the scaling
df_model_data_limb <- bind_rows(data_limb_n, df_b_limb)
scaled_limb <- scale_data_manual(df_model_data_limb, "type") |>
  as_tibble()

scaled_limb_data <- scaled_limb |>
  filter(type == "data") |>
  select(-type)

scaled_limb_data_model <- scaled_limb |>
  filter(type == "model") |>
  select(-type)
```

```{r, eval=knitr::is_html_output()}
#| label: langevitour-limb-tsne-author-proj

data_limb_n <- data_limb_n |>
  select(-type) |>
  mutate(type = as.character(tsne_limb_scaled_with_cluster$cluster.ids))

df_model_data_limb_n <- bind_rows(df_b_limb, data_limb_n)

langevitour::langevitour(df_model_data_limb_n[1:(length(df_model_data_limb_n)-1)],
                         lineFrom = trimesh_data_limb$from,
                         lineTo = trimesh_data_limb$to,
                         group = factor(df_model_data_limb_n$type,
                                        c("0", "1", "2", "3", "4", "5", "6", "model")),
                         levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"))
```
